Technical Report

### 2018-03-20 fully-abstract-comp/technical-report.tex
Finish component validity judgement.

We say that a component is valid ($\vdash \var{comp}$), iff:
\begin{mathpar}
  \inference{}{
    A_{\mathrm{code}},A_{\mathrm{data}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} z
  }
  \and
  \inference{
    c \in \overline{c_{\mathrm{import}}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} c
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{code}} & \perm \sqsubseteq \rx
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} ((\perm,\normal),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{data}} & \permbnf \sqsubseteq \rw&
    \lin = \linear \Rightarrow \emptyset \subset [\baddr,\eaddr] \subseteq A_{\mathrm{own}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} ((\perm,\lin),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} \vsc \\
    \sigma = \sigma_b + o & \nrcalls \leq o < \nrcalls + \nrclosures
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} \sealed{\sigma,\vsc}
  }
  \and
  \inference{
    \dom(\ms_{\mathrm{code}}) = [\baddr_{\mathrm{code}},\eaddr_{\mathrm{code}}] &
    \ms_{\mathrm{code}}(\baddr_{\mathrm{code}}) = \seal{\sigma_\baddr,\sigma_\baddr+\nrcalls+\nrclosures-1,\sigma_\baddr}\\
    \forall a \in [\baddr_{\mathrm{code}}+1,\eaddr_{\mathrm{code}}]\ldotp \ms_{\mathrm{code}}(a) \in \ints\\
    \exists \var{offset\_use\_site} \in [0\cdots \nrcalls-1] \fun \dom(\ms_{\mathrm{code}}) \\
    \forall a \in [\baddr_{\mathrm{code}}+1,\eaddr_{\mathrm{code}}-\calllen+1]\ldotp \ms_{\mathrm{code}}([a\cdots a+\calllen-1]) = \scall[0..\calllen-1]{o}{r_1}{r_2} \Rightarrow \var{offset\_use\_site}(o) =a\\
    \exists A_\mathrm{own} : \dom(\ms_{\mathrm{data}}) \rightarrow \powerset{\dom(\ms_{\mathrm{data}})} & \dom(\ms_{\mathrm{data}}) = \biguplus_{a \in \dom(\ms_{\mathrm{data}})} A_{\mathrm{own}}(a) \\
    \forall a \in \dom(\ms_{\mathrm{data}})\ldotp \dom(\ms_{\mathrm{code}}),\dom(\ms_{\mathrm{data}}),A_{\mathrm{own}}(a),\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}}\ms_{\mathrm{data}}(a)\\
  }{
    \vdash (\ms_{\mathrm{code}},\ms_{\mathrm{data}},\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigma_\baddr,\nrcalls,\nrclosures)
  }
\end{mathpar}

>>>>

We define inductively when a component is valid ($\vdash \var{comp}$) by the below inference rules:
\begin{mathpar}
  \inference{}{
    A_{\mathrm{code}},A_{\mathrm{data}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} z
  }
  \and
  \inference{
    c \in \overline{c_{\mathrm{import}}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} c
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{code}} & \perm \sqsubseteq \rx
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} ((\perm,\normal),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{data}} & \permbnf \sqsubseteq \rw&
    \lin = \linear \Rightarrow \emptyset \subset [\baddr,\eaddr] \subseteq A_{\mathrm{own}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} ((\perm,\lin),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} \vsc \\
    \sigma = \sigma_b + o & \nrcalls \leq o < \nrcalls + \nrclosures
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}} \sealed{\sigma,\vsc}
  }
  \and
  \inference{
    \dom(\ms_{\mathrm{code}}) = [\baddr_{\mathrm{code}},\eaddr_{\mathrm{code}}] &
    \ms_{\mathrm{code}}(\baddr_{\mathrm{code}}) = \seal{\sigma_\baddr,\sigma_\baddr+\nrcalls+\nrclosures-1,\sigma_\baddr}\\
    \forall a \in [\baddr_{\mathrm{code}}+1,\eaddr_{\mathrm{code}}]\ldotp \ms_{\mathrm{code}}(a) \in \ints\\
    \exists \var{offset\_use\_site} \in [0\cdots \nrcalls-1] \fun \dom(\ms_{\mathrm{code}}) \\
    \forall a \in [\baddr_{\mathrm{code}}+1,\eaddr_{\mathrm{code}}-\calllen+1]\ldotp \ms_{\mathrm{code}}([a\cdots a+\calllen-1]) = \scall[0..\calllen-1]{o}{r_1}{r_2} \Rightarrow \var{offset\_use\_site}(o) =a\\
    \exists A_\mathrm{own} : \dom(\ms_{\mathrm{data}}) \rightarrow \powerset{\dom(\ms_{\mathrm{data}})} & \dom(\ms_{\mathrm{data}}) = \biguplus_{a \in \dom(\ms_{\mathrm{data}})} A_{\mathrm{own}}(a) \\
    \forall a \in \dom(\ms_{\mathrm{data}})\ldotp \dom(\ms_{\mathrm{code}}),\dom(\ms_{\mathrm{data}}),A_{\mathrm{own}}(a),\overline{c_{\mathrm{import}}},\sigma_\baddr,\nrcalls,\nrclosures \vdash_{\mathrm{comp-value}}\ms_{\mathrm{data}}(a)\\
    \overline{\dom(\ms_{\mathrm{code}}), \dom(\ms_{\mathrm{data}}), \emptyset, \overline{c_{\mathrm{import}}}, \sigma_\baddr, \nrcalls, \nrclosures \vdash_{\mathrm{comp-value}} c_{\mathrm{export}}}
  }{
    \vdash (\ms_{\mathrm{code}},\ms_{\mathrm{data}},\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigma_\baddr,\nrcalls,\nrclosures)
  }
\end{mathpar}
